Imputation

### 2017-07-24 imputation.Rmd
draft2

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = "center", fig.width = 15, fig.asp = 0.7)
```

@@

```{r}
system.time(
  bedfile2 <- snp_beagleImpute(beagle.path = BEAGLE,
                               plink.path = PLINK,
                               bedfile.in = bedfile,
                               memory.max = 30,
                               ncores = NCORES)
) # 14.6 / 14.8 /  hours
```

@@

mean(X_beagle[indNA] != X[indNA]) # 3.1 / 3.1 / %
table(X_beagle[indNA], X[indNA])
```

@@

```{r}
system.time(
  infos <- snp_fastImpute(GNA, infos.chr = popres$map$chromosome, ncores = NCORES)
) # Previous runs: 42 / 47 /  minutes
```

```{r, fig.asp=1}
# Errors
mean(XNA[indNA] != X[indNA]) # 4.7 / 4.8 /  %
table(XNA[indNA], X[indNA])

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.align = "center", out.width = "70%",
                      fig.width = 15, fig.asp = 0.7)
```

@@

```{r}
system.time(
  bedfile2 <- snp_beagleImpute(beagle.path = BEAGLE,
                               plink.path = PLINK,
                               bedfile.in = bedfile,
                               memory.max = 30,
                               ncores = NCORES)
) # 14.6 / 14.8 / 14.8 hours
```

@@

mean(X_beagle[indNA] != X[indNA]) # 3.1 / 3.1 / 3.1 %
table(X_beagle[indNA], X[indNA])
```

@@

```{r}
system.time(
  infos <- snp_fastImpute(GNA, infos.chr = popres$map$chromosome, ncores = NCORES)
) # Previous runs: 42 / 47 / 47 minutes
```

```{r, fig.asp=1}
# Errors
mean(XNA[indNA] != X[indNA]) # 4.7 / 4.8 / 4.8 %
table(XNA[indNA], X[indNA])
